### 2016-03-29 Chapters/chap2/manuscript.tex
Change to bib

We focus here on the rates of triplet exchange between a naphthalene donor and a benzaldehyde acceptor linked by a variety of bridging units.
\begin{center}
\includegraphics[width=0.50\columnwidth]{Chapters/chap2/Scheme1}
\end{center}
Triplet energy exchange in these systems occurs via the through-space Dexter mechanism\cite{Dexter:1952}.
This is a short-ranged interaction involving the simultaneous exchange of two electrons between the
donor and acceptor moieties.
Systems such as these formed the basis of a series of experiments by  Closs and Miller\cite{miller1984intramolecular}
in which they verified the existence of the Marcus inverted regime
and serve as crucial benchmarks for testing new theoretical models for computing
energy and charge transfer rates\cite{subotnik2008constructing,subotnik2009initial,Subotnik:2010}.

A number of years ago,  we developed a time-convolutionless  master equation approach for computing
state-to-state rates in which the coupling between  states depends upon the
nuclear coordinates\cite{pereverzev:104906}. This approach incorporates a fully quantum
mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
well-known Marcus expression in the semiclassical limit.  The model is parameterized by the
vibrational normal mode frequencies, and the electronic energies and energy derivatives
at a reference configuration.  The approach has been used by our group to compute state-to-state
transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
\cite{Tamura08,tamura:021103,Bittner:2014ab,Jaykrishna-Singh:2009ly}.
This paper represents the first time we have used this approach within the context of a fully {\em ab initio} quantum
chemical model.   As such, this present work provides an important benchmark of the approach since all parameters will be determined
using state-of-the-art quantum chemical methods
and results compared to both theoretical and experimental
rates.

Central to the work presented here is the use of a diabatization scheme for determining
donor and acceptor states in a molecular unit.  We benchmark the approach
by computing the  triplet energy transfer rates for a series of donor-bridge-acceptor molecules
originally studied by Closs\cite{miller1984intramolecular}.  The triplet energy transfer rates computed using our approach
compare well against both the experimental rates and with
more recent theoretical rates presented by Subotnik {\em et al.}
\cite{subotnik2008constructing,subotnik2009initial,Subotnik:2010}.
An important component of our analysis is the use of a projection operator scheme
that parses out specific internal nuclear motions that accompany
the electronic transition.
Similar decomposition schemes have been presented by Burghardt
 \cite{Cederbaum:2005,gindensperger:144103,gindensperger:144104,PhysRevLett.94.113003}
 and the approach used here builds upon the method given in Ref.~\cite{pereverzev:034104}.
 By analyzing the electron-phonon couplings, we can
discern a reduced set of motions that are responsible for coupling between the donor and
acceptor states.

@@

We now separate Eq.~\ref{ham1} into diagonal and
off-diagonal terms
\begin{eqnarray}
\hat  H = \hat H_{o} + \hat V
\end{eqnarray}
and perform a polaron transform
using the unitary transformation~\cite{grover:2099,rice:2504,pereverzev:104906}.
\begin{eqnarray}
U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
n|(a^{\dagger}_i-a_i)}
 \nonumber \\
&=&
\sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
\label{unitary}
\end{eqnarray}
under which the transformed Hamiltonian is written in terms of the
diagonal elements
\begin{eqnarray} \tilde H_0=U^{-1}H_0U
=\sum_n\tilde\epsilon_n |n\rangle \langle
n|+\sum_i\omega_ia^{\dagger}_ia_i,
 \end{eqnarray}
with  the renormalized electronic energies,
\begin{eqnarray}
\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
\end{eqnarray}
and off-diagonal terms,
\begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
\label{opm}
\end{eqnarray}
In the transformed (or dressed) picture the electronic transition from state
$|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
normal phonon modes.  Transforming to the interaction representation
and performing a trace over the phonons gives the spectral density in
terms of the autocorrelation of the electron-phonon coupling
operators.
\begin{eqnarray}
S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{spec-dens}
\end{eqnarray}
Here, $\hat V_{nm}(t)$ is the electron-phonon coupling term in the Heisenberg representation and
$\langle \cdots \rangle$ denotes a thermal average over the
vibrational degrees of freedom.
The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
Ref.~\cite{pereverzev:104906}.

@@

In Ref.~\cite{pereverzev:104906}, Pereverzev and Bittner derived
a non-Markovian, time-convolutionless form of the Pauli master
equation (TCLME)  for general system described by Eq.~\ref{ham1}.
\begin{eqnarray}
\frac{dP_{n}}{dt} = \sum_{m} W_{nm}(t)P_{m}(t) - \left(\sum_{m} W_{mn}(t)\right)P_{n}(t)
\end{eqnarray}
where the time-dependent rates are given by
\begin{eqnarray}
W_{nm}(\tau)=2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
\label{rate-expression}
\end{eqnarray}
In the limit that $\tau\to\infty$, Eq.~\ref{rate-expression} gives the Fermi's Golden Rule expression for the
transition rate,
\begin{eqnarray}
k_{nm}=2{\rm Re}\int_{0}^{\infty}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
\label{gr-expression}
\end{eqnarray}

@@

The difficulty in using this approach is that
it requires both diagonal (${\mathbf g}_{nn}$) and off-diagonal  (${\mathbf g}_{nm}$) derivative couplings between
adiabatic states.    In the following section, we discuss how we have used the Edmiston-Ruedenberg localization scheme
to estimate the couplings\cite{RevModPhys.35.457}.   We also
present how one can construct a reduced set of harmonic modes that
fully capture the electron/nuclear coupling.
\subsection{Parameterization From Quantum Chemistry}

@@

Using the ER localization approach, all parameters needed for our model can be  obtained from
standard  quantum chemical packages.   The vertical energies, $\epsilon_{a}$
and $\epsilon_{b}$ are obtained from single point CI(S) calculations at a given
reference geometry.   We then project the energy gradients onto the vibrational normal
coordinates to obtain the electron-phonon coupling constants.  Either the Boys or ER
localization scheme can be use to compute the mixing
angles for constructing diabatic states. For all calculations shown here we
used the qChem 4.0 code and employed the 6-31G(d){*}{*} basis set
in order to compare our results  with  Ref. \cite{Subotnik:2010}.

@@

\begin{sidewaystable}
% \begin{table*}[t]
\begin{centering}
\begin{tabular}{llccc|ccc}
\hline \hline
 & & \multicolumn{3}{c}{Rates (s$^{-1}$) }& \\
                &                                                                &   Expt.                 &        Marcus Theory   & This work      & \multicolumn{3}{c}{Marcus theory parameters} \\
 Bridge   &  Structure                                                &        Ref.~\cite{closs1988determination,closs1989connection} &              Ref. \cite{Subotnik:2010}  &                  &      $\lambda$ (eV)  &  $\Delta \epsilon$ (eV)  &  $V_{ab}$ ($\mu$eV) \\
\hline
 c-1,3ea  &  \includegraphics[height=.60cm,width=2cm]{Chapters/chap2/Table1-c13ea.pdf}  &                     3.3E9  &                     3.9E9  &          2.2E9  &           0.823  &           -0.612  &      470.1  \\
\hline
 c-1,3ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-c13ee.pdf}  &                     7.7E9  &                    2.1E10  &         2.8E10  &           0.810  &           -0.580  &     1687.3  \\
\hline
 c-1,4ea  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-c14ea.pdf}  &                     4.0E7  &                     1.3E7  &          1.8E7  &           0.817  &           -0.604  &      43.20 \\
\hline
 c-1,4ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-c14ee.pdf}  &                     1.3E9  &                     3.9E9  &          3.6E9  &           0.826  &           -0.642  &      605.8  \\
\hline
 d-2,6ae  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d26ae.pdf}  &                     1.3E5  &                     1.0E4  &          4.7E4  &           0.836  &           -0.577  &    2.239  \\
\hline
d-2,6ea  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d26ea.pdf}  &                     7.0E5  &                     3.9E4  &          5.8E4  &            0.821  &            -0.609  &    2.414  \\
\hline
 d-2,6ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-d26ee.pdf}  &                     3.1E6  &                     5.0E6  &          4.8E6  &           0.810  &           -0.581  &     22.12  \\
\hline
 d-2,7ae  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d27ae.pdf}  &                     1.1E7  &                     2.8E7  &          3.0E7  &           0.826  &           -0.605  &     55.16   \\
\hline
 d-2,7ea  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d27ea.pdf}  &                     1.5E7  &                     1.8E7  &          4.3E7  &           0.817  &           -0.605  &     65.85  \\
\hline
 d-2,7ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-d27ee.pdf}  &                     9.1E7  &                     3.5E8  &          3.4E8  &           0.831  &           -0.648  &     185.1  \\
\hline
 M        &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-M.pdf}      &                    5.0E10  &                      n.r.  &          1.2E9  &              0.896  &      -0.636  &      357.0 \\
\hline
\end{tabular}

\par\end{centering}
\caption{Comparison of triplet-triplet energy transfer rates obtained from our  approach,  Marcus rates are
from Ref.\cite{Subotnik:2010}
and experimental rates from Refs.\cite{closs1988determination,closs1989connection}.   The experimental error is estimated to be 20\% in each
case studied here.
The $V_{ab}$ are the diabatic couplings obtained using  Edmiston-Ruedenberg diabatization.
In each case, D =4-benzophenonyl and A = 2-napthyl.  n.r. = Not Reported.
}
\label{summarytable}
% \end{table*}
\end{sidewaystable}

\begin{figure}[t]
\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure3}
\caption{Comparison between predicted (TCLME) rate constants and the experimental rates from Ref.\cite{miller1984intramolecular}.  With exception of
the methyl and D-2,6-ea bridged cases, the TCLME results are in good agreement with the experimental results.  }\label{compare}
\end{figure}

In general, our results and those in Ref.\cite{Subotnik:2010} agree with each other well and both are
comparable to the experimental results which report an estimated error of 10-20\% in the
rate for each case presented here.  Furthermore,  all theoretical values were computed
in the absence of solvent environment, whereas the experiments were all performed in benzene solvent at a standard temperature.
However,  there is considerable disagreement between the experimental and theoretical results for
the d-2,6ea and methyl (M) bridged cases.   For the d-2,6ea bridge,  our results are similar to the
Marcus theory rates given in Ref. \cite{Subotnik:2010}.  In this case, the
 the ER localization gives a  small diabatic coupling
 % $V_{ab} = 4.4\times 10^{-6}$eV
 and it was  difficult to obtain converged localized states.
In the case of the methyl-bridge,  there is a significant change in the geometry between donor and acceptor states.
As a result,  the potential surfaces are no longer parabolic
and the Condon approximation breaks down.\cite{Subotnik:2010}

@@

As an illustrative example of our approach, we consider the
first few collective modes for the c-1,4ee and d-2,5ae cases.
 In Fig.~\ref{LanczosModes_chap2}
we show the projection of the primary coupling mode onto the
coordinate frame of each molecule.  The vectors indicate the direction
of the electron-phonon coupling vectors projected onto the Cartesian displacement
vectors of the individual atoms.   In each case, the primary
coupling mode involves the  $b_{2u}$ in plane C=C stretching motions of the naphthalene donor and the
 in-plane $\nu_{8}$ (in the Mulliken numbering scheme) ring-squeezing motions of the benzaldehyde acceptor\cite{doi:10.1021/jp961282l}.
It is interesting to note
that $^{3}B_{2u}$ is also the symmetry of the first triplet $\pi-\pi^{*}$ excited state in naphthalene \cite{doi:10.1021/j100066a007},
Moreover, if we were to approximate benzaldehyde as a $C_{2v}$ molecule, taking the aldehyde as local site,
the resulting first triplet $\pi-\pi^{*}$ is the product of a $b_{1}$ HOMO and a $b_{1}$ LUMO giving a state in the
  $a_{1}$ irreducible representation. This is the same irreducible representation one obtains for the $\nu_{8}$
  mode, approximating it as a symmetric stretching mode.
This suggests the existence of underlying symmetry selection or propensity rule in determining the coupling modes.

@@

@@

% \bibliography{../References-local}
% \bibliographystyle{plainnat}
% \chapterbib
\providecommand*\mcitethebibliography{\thebibliography}
\csname @ifundefined\endcsname{endmcitethebibliography}
  {\let\endmcitethebibliography\endthebibliography}{}
\begin{mcitethebibliography}{27}
\providecommand*\natexlab[1]{#1}
\providecommand*\mciteSetBstSublistMode[1]{}
\providecommand*\mciteSetBstMaxWidthForm[2]{}
\providecommand*\mciteBstWouldAddEndPuncttrue
  {\def\EndOfBibitem{\unskip.}}
\providecommand*\mciteBstWouldAddEndPunctfalse
  {\let\EndOfBibitem\relax}
\providecommand*\mciteSetBstMidEndSepPunct[3]{}
\providecommand*\mciteSetBstSublistLabelBeginEnd[3]{}
\providecommand*\EndOfBibitem{}
\mciteSetBstSublistMode{f}
\mciteSetBstMaxWidthForm{subitem}{(\alph{mcitesubitemcount})}
\mciteSetBstSublistLabelBeginEnd
  {\mcitemaxwidthsubitemform\space}
  {\relax}
  {\relax}

% \begin{thebibliography}{27}
\bibitem[Marcus(1956)]{marcus1956theory}
Marcus,~R.~A. On the Theory of Oxidation-Reduction Reactions Involving Electron
  Transfer. I. \emph{J. Chem. Phys.} \textbf{1956}, \emph{24},
  966--978\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Marcus(1965)]{marcus1965theory}
Marcus,~R.~A. On the Theory of Electron-Transfer Reactions. VI. Unified
  Treatment for Homogeneous and Electrode Reactions. \emph{J. Chem. Phys} \textbf{1965}, \emph{43}, 679\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Marcus(1993)]{marcus1993electron}
Marcus,~R.~A. Electron transfer reactions in chemistry. Theory and experiment.
  \emph{Rev. Mod.  Phys.} \textbf{1993}, \emph{65}, 599--610\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Dexter(1953)]{Dexter:1952}
Dexter,~D.~L. A Theory of Sensitized Luminescence in Solids. \emph{J. Chem. Phys.} \textbf{1953}, \emph{21}, 836--850\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Miller et~al.(1984)Miller, Calcaterra, and
  Closs]{miller1984intramolecular}
Miller,~J.; Calcaterra,~L.; Closs,~G. Intramolecular long-distance electron
  transfer in radical anions. The effects of free energy and solvent on the
  reaction rates. \emph{J.  Am.  Chem.  Soc.}
  \textbf{1984}, \emph{106}, 3047--3049\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Subotnik et~al.(2008)Subotnik, Yeganeh, Cave, and

>>>>

We focus here on the rates of triplet exchange between a naphthalene donor and a benzaldehyde acceptor linked by a variety of bridging units.
\begin{center}
\includegraphics[width=0.50\columnwidth]{Chapters/chap2/Scheme1}
\end{center}
Triplet energy exchange in these systems occurs via the through-space Dexter mechanism\cite{dexter1953theory}.
This is a short-ranged interaction involving the simultaneous exchange of two electrons between the
donor and acceptor moieties.
Systems such as these formed the basis of a series of experiments by  Closs and Miller\cite{miller1984intramolecular}
in which they verified the existence of the Marcus inverted regime
and serve as crucial benchmarks for testing new theoretical models for computing
energy and charge transfer rates\cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.

A number of years ago,  we developed a time-convolutionless  master equation approach for computing
state-to-state rates in which the coupling between  states depends upon the
nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum
mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
well-known Marcus expression in the semiclassical limit.  The model is parameterized by the
vibrational normal mode frequencies, and the electronic energies and energy derivatives
at a reference configuration.  The approach has been used by our group to compute state-to-state
transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
\cite{tamura2008phonon,tamura2007exciton,bittner2014noise,singh2009fluorescence}.
This paper represents the first time we have used this approach within the context of a fully {\em ab initio} quantum
chemical model.   As such, this present work provides an important benchmark of the approach since all parameters will be determined
using state-of-the-art quantum chemical methods
and results compared to both theoretical and experimental
rates.

Central to the work presented here is the use of a diabatization scheme for determining
donor and acceptor states in a molecular unit.  We benchmark the approach
by computing the  triplet energy transfer rates for a series of donor-bridge-acceptor molecules
originally studied by Closs\cite{miller1984intramolecular}.  The triplet energy transfer rates computed using our approach
compare well against both the experimental rates and with
more recent theoretical rates presented by Subotnik {\em et al.}
\cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.
An important component of our analysis is the use of a projection operator scheme
that parses out specific internal nuclear motions that accompany
the electronic transition.
Similar decomposition schemes have been presented by Burghardt
 \cite{cederbaum2005short,gindensperger2006shortI,gindensperger2006shortII,cederbaum2005short}
 and the approach used here builds upon the method given in Ref.~\cite{pereverzev2009energy}.
 By analyzing the electron-phonon couplings, we can
discern a reduced set of motions that are responsible for coupling between the donor and
acceptor states.

@@

We now separate Eq.~\ref{ham1} into diagonal and
off-diagonal terms
\begin{eqnarray}
\hat  H = \hat H_{o} + \hat V
\end{eqnarray}
and perform a polaron transform
using the unitary transformation~\cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
\begin{eqnarray}
U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
n|(a^{\dagger}_i-a_i)}
 \nonumber \\
&=&
\sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
\label{unitary}
\end{eqnarray}
under which the transformed Hamiltonian is written in terms of the
diagonal elements
\begin{eqnarray} \tilde H_0=U^{-1}H_0U
=\sum_n\tilde\epsilon_n |n\rangle \langle
n|+\sum_i\omega_ia^{\dagger}_ia_i,
 \end{eqnarray}
with  the renormalized electronic energies,
\begin{eqnarray}
\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
\end{eqnarray}
and off-diagonal terms,
\begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
\label{opm}
\end{eqnarray}
In the transformed (or dressed) picture the electronic transition from state
$|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
normal phonon modes.  Transforming to the interaction representation
and performing a trace over the phonons gives the spectral density in
terms of the autocorrelation of the electron-phonon coupling
operators.
\begin{eqnarray}
S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{spec-dens}
\end{eqnarray}
Here, $\hat V_{nm}(t)$ is the electron-phonon coupling term in the Heisenberg representation and
$\langle \cdots \rangle$ denotes a thermal average over the
vibrational degrees of freedom.
The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
Ref.~\cite{pereverzev2006time}.

@@

In Ref.~\cite{pereverzev2006time}, Pereverzev and Bittner derived
a non-Markovian, time-convolutionless form of the Pauli master
equation (TCLME)  for general system described by Eq.~\ref{ham1}.
\begin{eqnarray}
\frac{dP_{n}}{dt} = \sum_{m} W_{nm}(t)P_{m}(t) - \left(\sum_{m} W_{mn}(t)\right)P_{n}(t)
\end{eqnarray}
where the time-dependent rates are given by
\begin{eqnarray}
W_{nm}(\tau)=2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
\label{rate-expression}
\end{eqnarray}
In the limit that $\tau\to\infty$, Eq.~\ref{rate-expression} gives the Fermi's Golden Rule expression for the
transition rate,
\begin{eqnarray}
k_{nm}=2{\rm Re}\int_{0}^{\infty}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
\label{gr-expression}
\end{eqnarray}

@@

The difficulty in using this approach is that
it requires both diagonal (${\mathbf g}_{nn}$) and off-diagonal  (${\mathbf g}_{nm}$) derivative couplings between
adiabatic states.    In the following section, we discuss how we have used the Edmiston-Ruedenberg localization scheme
to estimate the couplings\cite{edmiston1963localized}.   We also
present how one can construct a reduced set of harmonic modes that
fully capture the electron/nuclear coupling.
\subsection{Parameterization From Quantum Chemistry}

@@

Using the ER localization approach, all parameters needed for our model can be  obtained from
standard  quantum chemical packages.   The vertical energies, $\epsilon_{a}$
and $\epsilon_{b}$ are obtained from single point CI(S) calculations at a given
reference geometry.   We then project the energy gradients onto the vibrational normal
coordinates to obtain the electron-phonon coupling constants.  Either the Boys or ER
localization scheme can be use to compute the mixing
angles for constructing diabatic states. For all calculations shown here we
used the qChem 4.0 code and employed the 6-31G(d){*}{*} basis set
in order to compare our results  with  Ref. \cite{subotnik2010predicting}.

@@

\begin{sidewaystable}
% \begin{table*}[t]
\begin{centering}
\begin{tabular}{llccc|ccc}
\hline \hline
 & & \multicolumn{3}{c}{Rates (s$^{-1}$) }& \\
                &                                                                &   Expt.                 &        Marcus Theory   & This work      & \multicolumn{3}{c}{Marcus theory parameters} \\
 Bridge   &  Structure                                                &        Ref.~\cite{closs1988determination,closs1989connection} &              Ref. \cite{subotnik2010predicting}  &                  &      $\lambda$ (eV)  &  $\Delta \epsilon$ (eV)  &  $V_{ab}$ ($\mu$eV) \\
\hline
 c-1,3ea  &  \includegraphics[height=.60cm,width=2cm]{Chapters/chap2/Table1-c13ea.pdf}  &                     3.3E9  &                     3.9E9  &          2.2E9  &           0.823  &           -0.612  &      470.1  \\
\hline
 c-1,3ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-c13ee.pdf}  &                     7.7E9  &                    2.1E10  &         2.8E10  &           0.810  &           -0.580  &     1687.3  \\
\hline
 c-1,4ea  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-c14ea.pdf}  &                     4.0E7  &                     1.3E7  &          1.8E7  &           0.817  &           -0.604  &      43.20 \\
\hline
 c-1,4ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-c14ee.pdf}  &                     1.3E9  &                     3.9E9  &          3.6E9  &           0.826  &           -0.642  &      605.8  \\
\hline
 d-2,6ae  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d26ae.pdf}  &                     1.3E5  &                     1.0E4  &          4.7E4  &           0.836  &           -0.577  &    2.239  \\
\hline
d-2,6ea  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d26ea.pdf}  &                     7.0E5  &                     3.9E4  &          5.8E4  &            0.821  &            -0.609  &    2.414  \\
\hline
 d-2,6ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-d26ee.pdf}  &                     3.1E6  &                     5.0E6  &          4.8E6  &           0.810  &           -0.581  &     22.12  \\
\hline
 d-2,7ae  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d27ae.pdf}  &                     1.1E7  &                     2.8E7  &          3.0E7  &           0.826  &           -0.605  &     55.16   \\
\hline
 d-2,7ea  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d27ea.pdf}  &                     1.5E7  &                     1.8E7  &          4.3E7  &           0.817  &           -0.605  &     65.85  \\
\hline
 d-2,7ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-d27ee.pdf}  &                     9.1E7  &                     3.5E8  &          3.4E8  &           0.831  &           -0.648  &     185.1  \\
\hline
 M        &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-M.pdf}      &                    5.0E10  &                      n.r.  &          1.2E9  &              0.896  &      -0.636  &      357.0 \\
\hline
\end{tabular}

\par\end{centering}
\caption{Comparison of triplet-triplet energy transfer rates obtained from our  approach,  Marcus rates are
from ~Ref. \cite{subotnik2010predicting}
and experimental rates from Refs.\cite{closs1988determination,closs1989connection}.   The experimental error is estimated to be 20\% in each
case studied here.
The $V_{ab}$ are the diabatic couplings obtained using  Edmiston-Ruedenberg diabatization.
In each case, D =4-benzophenonyl and A = 2-napthyl.  n.r. = Not Reported.
}
\label{summarytable}
% \end{table*}
\end{sidewaystable}

\begin{figure}[t]
\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure3}
\caption{Comparison between predicted (TCLME) rate constants and the experimental rates from ~Ref. \cite{miller1984intramolecular}.  With exception of
the methyl and D-2,6-ea bridged cases, the TCLME results are in good agreement with the experimental results.  }\label{compare}
\end{figure}

In general, our results and those in ~Ref. \cite{subotnik2010predicting} agree with each other well and both are
comparable to the experimental results which report an estimated error of 10-20\% in the
rate for each case presented here.  Furthermore,  all theoretical values were computed
in the absence of solvent environment, whereas the experiments were all performed in benzene solvent at a standard temperature.
However,  there is considerable disagreement between the experimental and theoretical results for
the d-2,6ea and methyl (M) bridged cases.   For the d-2,6ea bridge,  our results are similar to the
Marcus theory rates given in Ref. \cite{subotnik2010predicting}.  In this case, the
 the ER localization gives a  small diabatic coupling
 % $V_{ab} = 4.4\times 10^{-6}$eV
 and it was  difficult to obtain converged localized states.
In the case of the methyl-bridge,  there is a significant change in the geometry between donor and acceptor states.
As a result,  the potential surfaces are no longer parabolic
and the Condon approximation breaks down.\cite{subotnik2010predicting}

@@

As an illustrative example of our approach, we consider the
first few collective modes for the c-1,4ee and d-2,5ae cases.
 In Fig.~\ref{LanczosModes_chap2}
we show the projection of the primary coupling mode onto the
coordinate frame of each molecule.  The vectors indicate the direction
of the electron-phonon coupling vectors projected onto the Cartesian displacement
vectors of the individual atoms.   In each case, the primary
coupling mode involves the  $b_{2u}$ in plane C=C stretching motions of the naphthalene donor and the
 in-plane $\nu_{8}$ (in the Mulliken numbering scheme) ring-squeezing motions of the benzaldehyde acceptor\cite{silva1996theoretical}.
It is interesting to note
that $^{3}B_{2u}$ is also the symmetry of the first triplet $\pi-\pi^{*}$ excited state in naphthalene \cite{aagren1994response},
Moreover, if we were to approximate benzaldehyde as a $C_{2v}$ molecule, taking the aldehyde as local site,
the resulting first triplet $\pi-\pi^{*}$ is the product of a $b_{1}$ HOMO and a $b_{1}$ LUMO giving a state in the
  $a_{1}$ irreducible representation. This is the same irreducible representation one obtains for the $\nu_{8}$
  mode, approximating it as a symmetric stretching mode.
This suggests the existence of underlying symmetry selection or propensity rule in determining the coupling modes.

@@

% \begin{}
% \bibliographystyle{chicago}
% \bibliography{Dbib}

@@

% \bibliography{../References-local}
% \bibliographystyle{plainnat}
% \chapterbib
% \providecommand*\mcitethebibliography{\thebibliography}
% \csname @ifundefined\endcsname{endmcitethebibliography}
%   {\let\endmcitethebibliography\endthebibliography}{}
% \begin{mcitethebibliography}{27}
% \providecommand*\natexlab[1]{#1}
% \providecommand*\mciteSetBstSublistMode[1]{}
% \providecommand*\mciteSetBstMaxWidthForm[2]{}
% \providecommand*\mciteBstWouldAddEndPuncttrue
%   {\def\EndOfBibitem{\unskip.}}
% \providecommand*\mciteBstWouldAddEndPunctfalse
%   {\let\EndOfBibitem\relax}
% \providecommand*\mciteSetBstMidEndSepPunct[3]{}
% \providecommand*\mciteSetBstSublistLabelBeginEnd[3]{}
% \providecommand*\EndOfBibitem{}
% \mciteSetBstSublistMode{f}
% \mciteSetBstMaxWidthForm{subitem}{(\alph{mcitesubitemcount})}
% \mciteSetBstSublistLabelBeginEnd
%   {\mcitemaxwidthsubitemform\space}
%   {\relax}
%   {\relax}

% % \begin{thebibliography}{27}
% \bibitem[Marcus(1956)]{marcus1956theory}
% Marcus,~R.~A. On the Theory of Oxidation-Reduction Reactions Involving Electron
%   Transfer. I. \emph{Journal Chem. Phys.} \textbf{1956}, \emph{24},
%   966--978\relax
% \mciteBstWouldAddEndPuncttrue
% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
% \EndOfBibitem
% \bibitem[Marcus(1965)]{marcus1965theory}
% Marcus,~R.~A. On the Theory of Electron-Transfer Reactions. VI. Unified
%   Treatment for Homogeneous and Electrode Reactions. \emph{J. Chem. Phys} \textbf{1965}, \emph{43}, 679\relax
% \mciteBstWouldAddEndPuncttrue
% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
% \EndOfBibitem
% \bibitem[Marcus(1993)]{marcus1993electron}
% Marcus,~R.~A. Electron transfer reactions in chemistry. Theory and experiment.
%   \emph{Rev. Mod.  Phys.} \textbf{1993}, \emph{65}, 599--610\relax
% \mciteBstWouldAddEndPuncttrue
% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
% \EndOfBibitem
% \bibitem[Dexter(1953)]{dexter1953theory}
% Dexter,~D.~L. A Theory of Sensitized Luminescence in Solids. \emph{J. Chem. Phys.} \textbf{1953}, \emph{21}, 836--850\relax
% \mciteBstWouldAddEndPuncttrue
% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
% \EndOfBibitem
% \bibitem[Miller et~al.(1984)Miller, Calcaterra, and
%   Closs]{miller1984intramolecular}
% Miller,~J.; Calcaterra,~L.; Closs,~G. Intramolecular long-distance electron
%   transfer in radical anions. The effects of free energy and solvent on the
%   reaction rates. \emph{J.  Am.  Chem.  Soc.}
%   \textbf{1984}, \emph{106}, 3047--3049\relax
% \mciteBstWouldAddEndPuncttrue
% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
